Scalar on Function Regression

### 2022-01-07 Presentation/slides.tex
presentation

	\begin{frame}{Random Function}
		Random element is a function $X : \Omega \rightarrow \mathcal{S}$ which is defined on a common probability space $(\Omega, \mathcal{F}, \mathbb{P})$ where $\Omega$ is a probability space with a $\sigma$-algebra $\mathcal{F}$ and a probability measure $\mathbb{{P}}.$
		\begin{itemize}
			\item If $\mathcal{S} = \mathbb{R}$ $\rightarrow$ X is a random variable
			\item If $\mathcal{S} = \mathbb{R}^{n}$ $\rightarrow$ X is a random vector
			\item If $\mathcal{S}$ is a space of functions, $X$ is called a random function
		\end{itemize}
	\end{frame}

	\begin{frame}{Random Function}
		Let $E$ be the index set and this can be described as
		$${\{X(t,\omega) : t \in E, \omega \in \Omega\},}$$
		where $X(t, \cdot)$ is $\mathcal{F}$-measurable function on the sample space $\Omega$.\\
		\begin{itemize}
			\item It can be shortened to $X(t)$ by omitting $\omega$
			\item The function is realized when the $X(t)$ have been observed for every $t \in E$
		\end{itemize}
	\end{frame}

	\begin{frame}{Square Integrable Function}
		If a function $f$ satisfies:
		$$\int_{0}^{1} \{f(t)\}^{2}dt < \infty$$
		the function $f$ is called square integrable function\\
		and in the set $\mathbb{L}^{2}[0,1]$.
		\begin{itemize}
			\item Without loss of generality, the interval is defined in $[0,1] $
			\item $\mathbb{L}^{2}$ is the set of all square integrable functions
			\item We focus on $\mathbb{L}^{2} [0,1]$ since the domain of our function is on the real line.
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Data Generating Process}
		With $X_{i}(t_{ij}) \in \mathbb{L}^{2}[0,1]$, the measurement of $X_{ij}$ is assumed to have noise with $\mathbb{E}(\epsilon)_{ij}=0$ and $\textbf{Var}(\epsilon_{ij}^{2})$, which are independent across $i$ and $j$.\\
		When the functional data has the same grid of domain, (SKIP)	
	\end{frame}

	\begin{frame}{Basis Expansion}
		Basis expansion is a linear combination of functions defining a function as described:
		$$X_{i}(t) \approx \sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad 1\leq i \leq n, \forall t \in E$$
		, where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion and $c_{ik}$ is the corresponding coefficient.
		\begin{itemize}
			\item To make the function smoother
			\item To replace the original scalar data $X_{n}(t_{jn})$ by a smaller collection of $c_{nm}$
		\end{itemize}		
	\end{frame}

	\begin{frame}{Two Typical Types of Basis Function}
		Fourier basis function is written as
		$$f(x) = a_{0} + \sum_{n=1}^{\infty}a_{n}cos(2\pi nx) + b_{n}sin(2\pi nx)$$	\\
		\vspace{2\baselineskip}
		B-spline basis function is a flexible curve defined by degree and knots. \\
		Each B-spline basis function, $i$-th B-spline basis function of degree $p$, $N_{i,p}(u)$ is defined on Cox-de Boor recursion formula.(Do you think I need to put the formula?)
	\end{frame}

@@

	\begin{frame}{Plots of Basis Functions}
		\begin{figure}
			\includegraphics[height = 4.5cm]{../Graphics/Bspline_Basis.pdf}
			\caption {Bspline Basis with order 9}
		\end{figure}
	\end{frame}

>>>>

	\begin{frame}{Random Function}
		Random element is a function $X : \Omega \rightarrow \mathcal{S}$ which is defined on a common probability space $(\Omega, \mathcal{F}, \mathbb{P})$ where $\Omega$ is a probability space with a $\sigma$-algebra $\mathcal{F}$ and a probability measure $\mathbb{{P}}.$
		\begin{itemize}
			\item If $\mathcal{S} = \mathbb{R}$ $\rightarrow$ X is a random variable
			\item If $\mathcal{S} = \mathbb{R}^{n}$ $\rightarrow$ X is a random vector
			\item If $\mathcal{S}$ is a space of functions, $X$ is called a \textbf{Random Function}
		\end{itemize}
	\end{frame}

	\begin{frame}{Random Function}
		Let $\mathbb{E}$ be the index set and this can be described as
		$${\{X(t,\omega) : t \in \mathbb{E}, \omega \in \Omega\},}$$
		where $X(t, \cdot)$ is $\mathcal{F}$-measurable function on the sample space $\Omega$.\\
		\begin{itemize}
			\item It can be shortened to $X(t)$ by omitting $\omega$
			\item The function is realized when the $X(t)$ have been observed for every $t \in \mathbb{E}$
		\end{itemize}
	\end{frame}

	\begin{frame}{Square Integrable Function}
		If a function $f$ satisfies:
		$$\int_{0}^{1} \{f(t)\}^{2}dt < \infty$$
		the function $f$ is called \textbf{Square Integrable Function}\\
		and in the set $\mathbb{L}^{2}[0,1]$.
		\begin{itemize}
			\item Without loss of generality, the interval is defined in $[0,1] $
			\item $\mathbb{L}^{2}$ is the set of all square integrable functions
			\item We focus on $\mathbb{L}^{2} [0,1]$ since the domain of our function is on the real line.
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Basis Expansion}
		\textbf{Basis Expansion} is a linear combination of functions defining a function as described:
		$$X_{i}(t) \approx \sum_{k=1}^{K} c_{ik}\phi_{k}(t), \quad 1\leq i \leq n, \forall t \in E$$
		, where $\phi_{k}(t)$ is the $k^{th}$ basis function of the expansion and $c_{ik}$ is the corresponding coefficient.
		\begin{itemize}
			\item To make the function smoother
			\item To replace the original scalar data $X_{n}(t_{jn})$ by a smaller collection of $c_{nm}$
		\end{itemize}		
	\end{frame}

	\begin{frame}{Two Typical Types of Basis Function}
		\textbf{Fourier Basis Function} is written as
		$$f(x) = a_{0} + \sum_{n=1}^{\infty}a_{n}cos(2\pi nx) + b_{n}sin(2\pi nx)$$	\\
		\vspace{2\baselineskip}
		\textbf{B-spline Basis Function} is a flexible curve defined by degree and knots. \\
		Each B-spline basis function, $i$-th B-spline basis function of degree $p$, $N_{i,p}(u)$ is defined on Cox-de Boor recursion formula.(Do you think I need to put the formula?)
	\end{frame}

@@

	\begin{frame}{Plots of Basis Functions}
		\begin{figure}
			\includegraphics[height = 4.5cm]{../Graphics/Bspline_Basis.pdf}
			\caption {Bspline basis functions with order 9}
		\end{figure}
	\end{frame}
